### 2013-08-21 main.tex
remove all occurences of i.e. and e.g. minor fixes

\begin{titlepage}
\begin{center}
\vspace*{1in}
\textbf{{\LARGE Dissertation}}
\par
\vspace{1.5in} {\large Andreas M\"uller}
 \par \vfill A Thesis submitted for the degree of Doctor of Philosophy
\par \vspace{0.5in}
Institute for Computer Science \par
Department IV, Autonomous Intelligent Systems
\par \vspace{0.5in}
Friedrich-Willhelm Universit\"at Bonn \par
\vspace{0.5in} September 2013 \end{center}

@@

%\listoffigures
%\listoftables
\chapter*{Abstract}

\chapter*{Acknowledgements}
First, I would like to thank my advisor Sven Behnke, who allowed me
to pursue my PhD in his department and who provided funding for my studies.
Juergen fuer review?

During my work on this dissertation, my ideas where shape by many of my fellow
students and researchers. First and foremost I am indept to Hannes Schulz,
whose feedback proved invaluable during my studies.
I would like to thank Christoph Lampert, for hosting me as visiting Researcher
at the IST Austria. His guidance and advice.

Carsten Rother, Sebastian Nowozin

Cristian Sminchisescu?
Phillip, Victoriia, Aurelien, Theo

I have been lucky to be a part of the scikit-learn community, whos developers
have been a constant source of encouragement and feedback to me. My understanding
of machine learning as well as software engineering has been greatly affected
by the constant exchange with Olivier Grisel, Lars Buitinck, Gael Varoquax,
Vlad Niculae, Mathieu Blondel, Gilles Louppe, Arnaud Joly and others.

@@

Last but not least I am greatful to Anna M\"uller for her support, encouragement and company
Thank you for giving me the strength needed for this endeavour.

@@

\chapter{Overview}
\include{intro.tex}

\chapter{Information Theoretic Clustering for Object Class Discovey}
\include{itm/paper}

@@

\chapter{Concepts and Implementation of Conditional Random Field-based Semantic Segmentation}\label{structured_pystruct}

@@

\chapter{Hierarchical Latent Variable Models for Semantic Segmentation}

>>>>

\begin{titlepage}
\begin{center}
\vspace*{1in}
\textbf{{\LARGE On Learning Structured Prediction For Semantic Segmentation}}
\par
\vspace{1.5in} {\large Andreas Christian M\"uller}
\par \vspace{0.5in}
Abteilung VI, Autonomie Intelligente Systeme \par
Institut f\"ur Informatik
\par \vspace{0.5in}
Friedrich-Willhelm Universit\"at Bonn \par
\vspace{0.5in} September 2013 \end{center}

@@

%\listoffigures
%\listoftables
\chapter*{Zusammenfassung}
\chapter*{Abstract}

\chapter*{Acknowledgements}
First, I would like to thank my advisor Sven Behnke, who allowed me
to pursue my PhD in his department and who provided funding for my studies.
I would also like to thank J\"urgen Gall for agreeing to be my second reader.

During my work on this dissertation, my ideas were shaped by many of my fellow
students and researchers. First and foremost I am in debt to Hannes Schulz,
whose feedback proved to be invaluable during my studies.
I would like to thank Christoph Lampert, for hosting me as a visiting researcher
at the IST Austria. His guidance and advice helped me in directing my further
research. My thanks are also extended to Sebastian Nowozin for his collaboration,
many helpful discussions, and advise.

I would also like to thank Carsten Rother for allowing me to work with him
at Microsoft Research Cambridge and hosting me there.

I have been lucky to be a part of the scikit-learn community, whose developers
have been a constant source of encouragement and feedback to me. My understanding
of machine learning as well as software engineering has been greatly affected
by the constant exchange with Olivier Grisel, Lars Buitinck, Gael Varoquax,
Vlad Niculae, Mathieu Blondel, Gilles Louppe, Arnaud Joly and others.

@@

Last but not least I am greatful to Anna M\"uller for her support,
encouragement and company. Thank you for giving me the strength needed for this
endeavour.

@@

\chapter{Overview}
\include{intro}

\chapter{Information Theoretic Clustering}
\include{itm/paper}

@@

\chapter{Concepts and Implementation of Conditional Random Field-based Semantic Segmentation}\label{ch:structured_pystruct}

@@

\chapter{Hierarchical Latent Variable Models for Semantic Segmentation}\label{ch:latent}

### 2013-08-21 mil/paper.tex
remove all occurences of i.e. and e.g. minor fixes

\subsection{Necessary Assumptions}\seclabel{assumptions}
If we allow instances inside bags and their labels to have arbitrary dependencies, we are trying to find
$y_1,\dotsc,y_r$ maximizing $p(y_1,\dotsc, y_r | x_1, \dotsc, x_r)$. This is a structured 
prediction problem for which there is no hope solving it, given only bag labels.
Therefore, as usual in multiple instance learning, we assume there is an underlying concept for instances,
i.\,e.\ the label of each instance depends only on this instance.
In other words, we assume $p(y_1,\dotsc, y_r | x_1, \dotsc, x_r)=p(y_1|x_1) \cdot p(y_r|x_r)$.

@@

\subsection{Independent Case}\seclabel{iid}
The simplest case in which learning instance prediction is possible is the case when instances are globally i.i.d.,
i.\,e.\ when instances inside a bag are independent of each other. This is a very strong assumption that might be
violated in practical applications. On the other hand, strong results can be proved in this setting.

@@

\begin{figure}[tbp]
	\begin{center}
		\includegraphics[width=.40 \linewidth]{images/gehler_decision_boundary.png}\hspace{5px}
		\includegraphics[width=.40 \linewidth]{images/gehler_instances.png}
	\end{center}
	\caption{Visualization of the dataset from \citet{gehler2007deterministic}. Left: Regions in $\mathbb{R}^2$
    corresponding to negative and positive instances. Right: Training points for 40\% positive rate. Red denotes negative
    bags, blue denotes positive bags. Crosses denote positive instances, circles negative instances.}
	\figlabel{gehler}

>>>>

\subsection{Necessary Assumptions}\seclabel{assumptions}
If we allow instances inside bags and their labels to have arbitrary dependencies, we are trying to find
$y_1,\dotsc,y_r$ maximizing $p(y_1,\dotsc, y_r | x_1, \dotsc, x_r)$. This is a structured 
prediction problem for which there is no hope solving it, given only bag labels.
Therefore, as usual in multiple instance learning, we assume there is an underlying concept for instances,
that is the label of each instance depends only on this instance.
In other words, we assume $p(y_1,\dotsc, y_r | x_1, \dotsc, x_r)=p(y_1|x_1) \cdot p(y_r|x_r)$.

@@

\subsection{Independent Case}\seclabel{iid}
The simplest case in which learning instance prediction is possible is the case when instances are globally i.i.d.,
that is when instances inside a bag are independent of each other. This is a very strong assumption that might be
violated in practical applications. On the other hand, strong results can be proved in this setting.

@@

\begin{figure}[tbp]
	\begin{center}
		\includegraphics[width=.40 \linewidth]{images/gehler_decision_boundary.png}\hspace{35px}
		\includegraphics[width=.40 \linewidth]{images/gehler_instances.png}
	\end{center}
	\caption{Visualization of the dataset from \citet{gehler2007deterministic}. Left: Regions in $\mathbb{R}^2$
    corresponding to negative and positive instances. Right: Training points for 40\% positive rate. Red denotes negative
    bags, blue denotes positive bags. Crosses denote positive instances, circles negative instances.}
	\figlabel{gehler}

### 2013-08-21 partial_supervision/paper.tex
minor layout issues in psl/mil
remove all occurences of i.e. and e.g. minor fixes

We formulate weakly supervised multi-class image segmentation as a multi-instance problem, based upon candidate segments.
In multi-instance learning~\citep{dietterich1997solving}, each training example is given as a multi-set of instances, called a bag.
Each instance is represented as a feature vector $x$ and a label $y$.
A bag is labeled positive if it contains at least one positive example, and negative otherwise.
During training, only the labels of the training bags, not of the instances inside the bags, are known.
The goal is to learn a classifier for unseen bags. 
Formally, let $\mathcal{X}$ be the set of instances. To simply notation, we assume that bags are simply sets, not multi-sets.
Then a bag is an element of the power set $2^\mathcal{X}$ and the task is
to learn a function
\begin{equation} f_{MI} \colon 2^\mathcal{X} \rightarrow \{-1,+1\}  \end{equation}
from a set of training examples of the form $(X_i,y_i)$ with bags $X_i \subset \mathcal{X}$ and labels $y_i \in \{-1,+1\}$.
The $f_{MI}$ function stems from the so-called underlying concept, given by an (unknown) function
$f_{I} \colon \mathcal{X} \rightarrow \{-1,+1\}$, with 
\begin{equation}\eqlabel{multi_instance}
f_{MI}(X)= \max_{x \in X} f_{I}(x).
\end{equation}

Sometimes, the goal of finding $f_{MI}$ is extended to finding labels not only
on bag-level but also for all the instances within a bag
\citep{liconvex2010,zha2008joint}, i.\,e.\ finding $f_{I}$.\\ 
Even though finding $f_{I}$ is sometimes included in the task statement, there
has been very little work that actually reported accuracy on instance label prediction. Part
of the reason for this might be that for many of the datasets used in
multi-instance learning no ground truth exists.

@@

@@

\citet{gaertner2002multi} introduced the concept of a multi-instance
kernel on bags, defined in terms of a kernel on instances. 
The basic principle of multi-instance kernel is similar to a soft-max over instances in
each bag. This can be viewed as approximating the kernel value of the ``closest pair'' given by two bags. They show that the multi-instance kernel
is able to separate bags if and only if the original kernel on instances is able to separate the underlying concepts.
The method of \citet{gaertner2002multi} has a particular appeal in that it neatly transforms a multi-instance problem into a standard
classification problem by changing the kernel. The downside of this approach is that it does
not directly label instances, only bags.
 %and that it assumes that instances inside a bag have i.i.d.
%labels.

@@

\section{Multi-Instance Kernels for Image Segmentation}
\subsection{Constraint Parametric Min Cuts (CPMC)}
To generate proposal segments, we use the Constraint Parametric Min Cut (CPCM) method from \citet{carreira2010constrained}. In CPMC, initial
segments are constructed graph cuts on the pixel grid. The energy function for these cuts uses pixel
color and the response of the global probability of boundary (gPb) detector~\citep{maire2008using}. As much as ten thousand initial segments are generated from foreground
and background seeds. A fast rejection based on segment size and ratio cut~\citep{wang2003image} reduced these to about 2000 overlapping
segments per image. Then, the segments are ranked according to a measure of object-likeness that is based on region and Gestalt properties.
This ranking is computed using an SVR model~\citep{carreira2010constrained}, which is available online.
For computing the global probability of boundary (gPb), we used the CUDA implementation
of \citet{catanzaro2009efficient}, instead of the original one, for speed.

@@

@@

\subsection{Combining Segments}\seclabel{combiningsegments}
The framework described above yields an image-level and a segment-level classification.
In our setup, each segment might be given multiple labels. To obtain a pixel-level object-class segmentation, we have to combine these. 
When building the segmentation for a given image, we only consider classes whose presence was predicted on image level.
Since we do not make use of the ground truth segmentation during training, we cannot learn an optimal combination as 
in \citet{li2010object} but perform a simple majority vote instead.
We merge segments into pixel-level class labels by setting
the label $y_x$ of a pixel $x$ according to
\begin{equation}
    y_x = \argmax_{y \in Y} \#\{S_i | p \in S_i \land y_{S_i}=y \},
\end{equation}
where $Y= \{$car, bike, person$ \}$, $S_i$ enumerates all segments within an
image and $y_{S_i}$ is the label of segment $S_i$. In words: each pixel is
assigned the class with the highest number of class segments containing it.
This simple heuristic yields good results in practice.

@@

\begin{table}
    \centering
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lccccccc}
    \toprule
        & SVM-SVR & EMDD & mi-SVM & MI-SVM & MICA & MIK & MIK-instance \\
    \cmidrule(rl){2-8}
    Musk1 & 87.9 &84.9 &  87.4 &  77.9     & 84.3 & 88.0& 88.0 \\
    Musk2 & 85.4 &84.8 &  83.6 &  84.3     & 90.5 & 89.3& 85.2 \\
    \bottomrule
    \end{tabularx}
    \caption{Bag level performance of various MIL algorithms on the standard Musk
    datasets. All but MIK provide instance-level labeling. }
    \tablabel{musk-acc}
\end{table}
We compared the performance of MIK, MIK-instance and state-of-the-art MI
methods on the Musk benchmark datasets~\citep{dietterich1997solving}, see
\tabref{musk-acc}. Results were obtained using 10-fold
cross-validation. While the computational complexity of MIK-instance is
very low compared to the other methods, it achieves competitive results.
Using instance-level labels results in a slight loss of accuracy of
MIK-instances, compared to MIK\@. This small degradation of performance is quite surprising, since the model was
not trained to provide any instance-level labels.

For multi-class image segmentation, it is beneficial to have a low witness
rate, i.\,e.\ only a few instances are assumed to be positive in a positive
bag. Since an object might not be very prominent in an image, only a fraction
of segments might correspond to the object.
\tabref{musk-witness} compares the witness rates of MIK-instance,
miSVM~\citep{andrews2003support} and SVR-SVM~\citep{liconvex2010} on the Musk
datasets. MIK-instance is able to achieve similar accuracy
with much less witnesses than the other methods.  Note that Musk1 consists of
very small bags while Musk2 contains significantly larger bags, more similar to the
image/segment setup.
\begin{table}
    \centering
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcccc}
    \toprule
    & \multicolumn2c{Musk1}  & \multicolumn2c{Musk2}  \\
                &accuracy & witness-rate & accuracy & witness-rate  \\
    \cmidrule(rl){2-3}
    \cmidrule(rl){4-5}
    mi-SVM      & 87.4          & 100\%               &  83.6          & 83.9\%\\
    SVM-SVR     & 87.9          & 100\%               &  85.4          & 89.5\%\\
    MIK-instance& 88.0          & 99\%                &  85.2          & 62.3\%\\
    \bottomrule
    \end{tabularx}
    \tablabel{musk-witness}
    \caption{MIL algorithms and the empirical witness rates of the
    classifiers.}
\end{table}

@@

%From each image, we extract overlapping object-like segments using constraint
%parametric min cuts (CPMC,\citet{carreira2010constrained}). We use the top 200 ranked segments and discard the
%rest.
%Each segment is described using SIFT~\citet{lowe2004distinctive} and
%ColorSIFT~\citet{van2009evaluating} features, from which we compute bag of
%visual word histograms as well as histograms of oriented
%gradients~\citet{dalal2005histograms}. We construct one MI-Kernel per
%feature which are combined using multiple kernel learning.
We adjusted parameters on a hold-out validation set using bag-level information and used the
training and test sets as given by the dataset.
It is straight-forward to extend the binary MIK method to the multi-class
setting using a one-vs-all strategy.
We train one MKL-SVM per class using MIK and predict class labels on segment level
using MIK-instance. If at least one SVM classifies a segment as positive,
it is associated with the most confident class. Otherwise, it is assigned
``background'' or no class.
This yields a classification of each segment into one of four classes: car, bike, person,
or background. We merge segments into pixel-level class labels as described
in \secref{combiningsegments}.

\begin{figure}[tbp]
	\begin{center}
        \includegraphics[width=35mm]{images/car1_img.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/car1_gt.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/car1_pos.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/car1_neg.png}\hspace*{0.7ex}\\
        \vspace{1mm}
        \includegraphics[width=35mm]{images/person1_img.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/person1_gt.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/person1_pos.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/person1_neg.png}\hspace*{0.7ex}
	\end{center}
        \caption{Qualitative results on on the Graz-02 dataset. Top: Results on
        category ``car''. Bottom: Results on category ``person''. From left to
        right: original image, ground truth segmentation, segment votes for
        correct class, segment votes against correct class (red many, blue few votes).}
	\figlabel{results}
\end{figure}

\begin{table}
    \centering
    \begin{tabularx}{\textwidth}{p{208pt}RRR}
    \toprule
                & car & bike & person \\
    \cmidrule(l){2-2}
    \cmidrule(l){3-3}
    \cmidrule(l){4-4}
        This work&   0.30&  0.45&  0.43 \\
        Best strongly supervised approaches~\citep{fulkerson2009class,schulz2011}&   0.72&  0.72&  0.66 \\
    \bottomrule
    \end{tabularx}
    \caption{Pixel-level accuracy on the Graz-02 dataset.}
    \tablabel{graz}
\end{table}
Per-class pixel accuracies are reported in \tabref{graz}; some qualitative results are shown in \figref{results}. The overall
accuracy on images labels, which is the task that was actually trained, is $90\%$.
While the performance of our multiple-instance based approach is far
from current methods that use pixel-level annotations, whose pixel-level accuracy is around $70\%$~\citep{fulkerson2009class,schulz2011} on pixel-level,
it can serve as a baseline for research on weakly supervised methods for image segmentation.

>>>>

We formulate weakly supervised multi-class image segmentation as a multi-instance problem, based upon candidate segments.
In multi-instance learning~\citep{dietterich1997solving}, each training example is given as a multi-set of instances, called a bag.
Each instance is represented as a feature vector $x$ and a label $y$.
A bag is labeled positive if it contains at least one positive example, and negative otherwise.
During training, only the labels of the training bags, not of the instances inside the bags, are known.
The goal is to learn a classifier for unseen bags. 
Formally, let $\mathcal{X}$ be the set of instances. To simplify notation, we assume that bags are simply sets, not multi-sets.
Then a bag is an element of the power set $2^\mathcal{X}$ and the task is
to learn a function
\begin{equation} f_{MI} \colon 2^\mathcal{X} \rightarrow \{-1,+1\}.  \end{equation}
Training examples are tuples $(X_i,y_i)$ of bags $X_i \subset \mathcal{X}$ and labels $y_i \in \{-1,+1\}$.
It is often assumed that the $f_{MI}$ function stems from a so-called underlying concept, given by an (unknown) function
$f_{I} \colon \mathcal{X} \rightarrow \{-1,+1\}$, with 
\begin{equation}\eqlabel{multi_instance}
f_{MI}(X)= \max_{x \in X} f_{I}(x).
\end{equation}

Sometimes, the goal of finding $f_{MI}$ is extended to finding labels not only
for new bags, but also for all the separate instances within a bag
\citep{liconvex2010,zha2008joint}, that is finding $f_{I}$.\\ 
Even though finding $f_{I}$ is sometimes included in the task statement, there
has been very little work that actually reported accuracy on instance label
prediction. Part of the reason for this might be that for many of the datasets
used in multi-instance learning no ground truth exists.

@@

%TODO theoretical part reference?
% TODO repetition below?

@@

\citet{gaertner2002multi} introduced the concept of a multi-instance
kernel on bags, defined in terms of a kernel on instances. 
The basic principle of multi-instance kernel is similar to a soft-max over instances in
each bag. This can be viewed as approximating the kernel value of the ``closest pair'' given by two bags. They show that the multi-instance kernel
is able to separate bags if and only if the original kernel on instances is able to separate the underlying concepts.
The method of \citet{gaertner2002multi} has a particular appeal in that it transforms a multi-instance problem into a standard
classification problem by changing the kernel. The downside of this approach is that it does
not directly label instances, only bags.
 %and that it assumes that instances inside a bag have i.i.d.
%labels.

@@

\section{Multi-Instance Kernels for Image Segmentation}
\subsection{Constraint Parametric Min Cuts (CPMC)}
To generate proposal segments, we use the Constraint Parametric Min Cut (CPCM) method from \citet{carreira2010constrained}. In CPMC, initial
segments are constructed graph cuts on the pixel grid. The energy function for these cuts uses pixel
color and the response of the global probability of boundary (gPb) detector~\citep{maire2008using}. As much as ten thousand initial segments are generated from foreground
and background seeds. A fast rejection based on segment size and ratio cut~\citep{wang2003image} reduced these to about 2000 overlapping
segments per image. Then, the segments are ranked according to a measure of object-likeness that is based on region and Gestalt properties.
This ranking is computed using an SVR model~\citep{carreira2010constrained}, which is available online.
For computing the global probability of boundary (gPb), we used the CUDA implementation
of \citet{catanzaro2009efficient}, which provides a speedup of two orders of magnitude over the original implementation.

@@

%TODO one classifier per class!

@@

\subsection{Combining Segments}\seclabel{combiningsegments}
The framework described above yields an image-level and a segment-level classification.
In our setup, each segment might be given multiple labels. %TODO explain!
To obtain a pixel-level object-class segmentation, we have to combine these. 
When building the segmentation for a given image, we only consider classes whose presence was predicted on image level.
Since we do not make use of the ground truth segmentation during training, we cannot learn an optimal combination as 
in \citet{li2010object} but perform a simple majority vote instead.
We merge segments into pixel-level class labels by setting
the label $y_x$ of a pixel $x$ according to
\begin{equation}
    y_x = \argmax_{y \in Y} \#\{S_i | p \in S_i \land y_{S_i}=y \},
\end{equation}
where $Y= \{$car, bike, person$ \}$, $S_i$ enumerates all segments within an %FIXME we didn't describe the dataset yet!
image and $y_{S_i}$ is the label of segment $S_i$. In words: each pixel is
assigned the class with the highest number of class segments containing it.
This simple heuristic yields good results in practice.

@@

\begin{table}
    \centering
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lccccccc}
    \toprule
        & SVM-SVR & EMDD & mi-SVM & MI-SVM & MICA & MIK & MIK-instance \\
    \cmidrule(rl){2-8}
    Musk1 & 87.9 &84.9 &  87.4 &  77.9     & 84.3 & 88.0& 88.0 \\
    Musk2 & 85.4 &84.8 &  83.6 &  84.3     & 90.5 & 89.3& 85.2 \\
    \bottomrule
    \end{tabularx}
    \caption{Bag level performance of various MIL algorithms on the standard Musk
    datasets. All but MIK provide instance-level labeling. \tablabel{muskacc}}

\end{table}
We compared the performance of MIK, MIK-instance and state-of-the-art MI
methods on the Musk benchmark datasets~\citep{dietterich1997solving}, see
\Tabref{muskacc}. Results were obtained using 10-fold
cross-validation. While the computational complexity of MIK-instance is
very low compared to the other methods, it achieves competitive results.
Using instance-level labels results in a slight loss of accuracy of
MIK-instances, compared to MIK\@. This small degradation of performance is quite surprising, since the model was
not trained to provide any instance-level labels.
i
For multi-class image segmentation, it is beneficial to have a low witness
rate, that is only a few instances are assumed to be positive in a positive
bag. Since an object might not be very prominent in an image, only a fraction
of segments might correspond to the object.
\Tabref{musk-witness} compares the witness rates of MIK-instance,
miSVM~\citep{andrews2003support} and SVR-SVM~\citep{liconvex2010} on the Musk
datasets. MIK-instance is able to achieve similar accuracy
with much less witnesses than the other methods.  Note that Musk1 consists of
very small bags while Musk2 contains significantly larger bags, more similar to the
image/segment setup.
\begin{table}
    \centering
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcccc}
    \toprule
    & \multicolumn2c{Musk1}  & \multicolumn2c{Musk2}  \\
                &accuracy & witness-rate & accuracy & witness-rate  \\
    \cmidrule(rl){2-3}
    \cmidrule(rl){4-5}
    mi-SVM      & 87.4          & 100\%               &  83.6          & 83.9\%\\
    SVM-SVR     & 87.9          & 100\%               &  85.4          & 89.5\%\\
    MIK-instance& 88.0          & 99\%                &  85.2          & 62.3\%\\
    \bottomrule
    \end{tabularx}
    \caption{MIL algorithms and the empirical witness rates of the
        classifiers.  \tablabel{musk-witness}}
\end{table}

@@

%From each image, we extract overlapping object-like segments using constraint
%parametric min cuts (CPMC,\citet{carreira2010constrained}). We use the top 200 ranked segments and discard the
%rest.
%Each segment is described using SIFT~\citet{lowe2004distinctive} and
%ColorSIFT~\citet{van2009evaluating} features, from which we compute bag of
%visual word histograms as well as histograms of oriented
%gradients~\citet{dalal2005histograms}. We construct one MI-Kernel per
%feature which are combined using multiple kernel learning.
We adjusted parameters on a hold-out validation set using bag-level information and used the
training and test sets as given by the dataset.
It is straight-forward to extend the binary MIK method to the multi-class
setting using a one-vs-all strategy.
We train one multiple kernel learning (MKL) SVM per class using MIK and predict class labels on segment level
using MIK-instance. If at least one SVM classifies a segment as positive,
it is associated with the most confident class. Otherwise, it is assigned
``background'' or no class.
This yields a classification of each segment into one of four classes: car, bike, person,
or background. We merge segments into pixel-level class labels as described
in \Secref{combiningsegments}.

\begin{figure}[tbp]
	\begin{center}
        \includegraphics[width=35mm]{images/car1_img.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/car1_gt.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/car1_pos.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/car1_neg.png}\hspace*{0.7ex}\\
        \vspace{1mm}
        \includegraphics[width=35mm]{images/person1_img.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/person1_gt.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/person1_pos.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/person1_neg.png}
	\end{center}
        \caption{Qualitative results on on the Graz-02 dataset. Top: Results on
        category ``car''. Bottom: Results on category ``person''. From left to
        right: original image, ground truth segmentation, segment votes for
        correct class, segment votes against correct class (red many, blue few votes).}
	\figlabel{results}
\end{figure}

\begin{table}
    \centering
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}p{208pt}ccc}
    \toprule
                & car & bike & person \\
    \cmidrule(l){2-2}
    \cmidrule(l){3-3}
    \cmidrule(l){4-4}
        This work&   0.30&  0.45&  0.43 \\
        Best strongly supervised approaches~\citep{fulkerson2009class,schulz2011}&   0.72&  0.72&  0.66 \\
    \bottomrule
    \end{tabularx}
    \caption{Pixel-level accuracy on the Graz-02 dataset.
        \tablabel{tab:graz}}
\end{table}
Per-class pixel accuracies are reported in \Tabref{tab:graz}; some qualitative results are shown in \figref{results}. The overall
accuracy on images labels, which is the task that was actually trained, is $90\%$.
While the performance of our multiple-instance based approach is far
from current methods that use pixel-level annotations, whose pixel-level accuracy is around $70\%$~\citep{fulkerson2009class,schulz2011} on pixel-level,
it can serve as a baseline for research on weakly supervised methods for image segmentation.

### 2013-08-21 pystruct/paper.tex
remove all occurences of i.e. and e.g. minor fixes

We also use another enhancement of the cutting plane algorithm introduced by
\citet{joachims2009cutting}, the caching oracle. For each training example $(x^i, y^i)$,
we maintain a set $C^i$ of the last $r$ results of loss-augmented inference
(line~\ref{get_cutting_plane} in Algorithm~\ref{alg_cutting_plane}).
For generating a new constraint $(\hat{y}^1, \dotsc, \hat{y}^n)$ we find
\[ 
    \hat{y}^i \leftarrow \argmax_{\hat{y}\in C^i} \sum_{i=1}^n \Delta(y^i, \hat{y}) - \left \langle \theta, \sum_{i=1}^n [\psi(x^i, y^i) - \psi(x^i, \hat{y})] \right \rangle
\]
by enumeration of $C^i$ and continue until line~\ref{convergence_check}.
Only if $\xi' - \xi < \epsilon$, i.e.\ the produced constraint is not violated, we
return to line~\ref{get_cutting_plane} and actually invoke the separation
oracle $I$.

>>>>

We also use another enhancement of the cutting plane algorithm introduced by
\citet{joachims2009cutting}, the caching oracle. For each training example $(x^i, y^i)$,
we maintain a set $C^i$ of the last $r$ results of loss-augmented inference
(line~\ref{get_cutting_plane} in Algorithm~\ref{alg_cutting_plane}).
For generating a new constraint $(\hat{y}^1, \dotsc, \hat{y}^n)$ we find
\[ 
    \hat{y}^i \leftarrow \argmax_{\hat{y}\in C^i} \sum_{i=1}^n \Delta(y^i, \hat{y}) - \left \langle \theta, \sum_{i=1}^n [\psi(x^i, y^i) - \psi(x^i, \hat{y})] \right \rangle
\]
by enumeration of $C^i$ and continue until line~\ref{convergence_check}.
Only if $\xi' - \xi < \epsilon$, that is the produced constraint is not violated, we
return to line~\ref{get_cutting_plane} and actually invoke the separation
oracle $I$.
